### 2016-11-20 src/local.tex
foo

\begin{lemma}
If $k \geq something$ then in any connected induced graph of $G^{M^*}_M$, 
$G'= G^{M^*}_M[U]$, 
$
\frac{w(U)}{w^*(U)} 
\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
$.
\end{lemma}

@@

>>>>

\begin{lemma}
\label{lemma:r}
If $k \geq something$ then in any connected induced graph of $G^{M^*}_M$, 
$G'= G^{M^*}_M[U]$, 
$
\frac{w(U)}{w^*(U)} 
\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
$.
\end{lemma}

@@

\begin{lemma}
\label{lemma:dec}
Given a parameter $k$, a bounded degree connected graph $G$, with a maximum
degree $d$ can be decomposed into connected components of size at least $k$, and at most
$d(k-1) + 1$.
\end{lemma}

\begin{proof}
We give a constructive proof.
Start constructing a connected component by adding adjacent vertices
one by one to the component and removing them from the graph.
If at some point, removing a vertex disconnect the graph, add all the small
components (of size less than $k$) to the constructed component and decompose
the large components (of size at least $k$) recursively.
Note that removing a vertex can break the graph to at most $d - 1$ additional
components.
\end{proof}

\begin{theorem}
The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
algorithm.
\end{theorem}

\begin{proof}
Combine lemma~\ref{lemma:dec}, and lemma~\ref{lemma:r}, 
and observe that the maximum degree in $G^{M^*}_M$ is $(C + 1)^C$ to
get the desire result.
\end{proof}
